### 2015-04-20 paper.tex
Add author names

{\Large \textbf\newline{Measurements on a 1:6 scale DOE Reference Model 2
cross-flow hydrokinetic turbine: Reynolds number dependence, near-wake dynamics,
and blade support strut losses}}
\newline
% Insert author names, affiliations and corresponding author email (do not include 
% titles, positions, or degrees).
\\
Name1 Surname\textsuperscript{1,\Yinyang},
Name2 Surname\textsuperscript{2,\Yinyang},
Name3 Surname\textsuperscript{2,\textcurrency a},
Name4 Surname\textsuperscript{2,\ddag},
Name5 Surname\textsuperscript{2,\ddag},
Name6 Surname\textsuperscript{2},
Name7 Surname\textsuperscript{3,*},
with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\bf{1} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bf{2} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip

>>>>

{\Large \textbf\newline{Measurements on a 1:6 scale DOE Reference Model 2
cross-flow hydrokinetic turbine: Reynolds number dependence, near-wake dynamics,
and blade support strut losses}}
\newline
% Insert author names, affiliations and corresponding author email (do not include 
% titles, positions, or degrees).
\\
Peter Bachant\textsuperscript{1,\Yinyang},
Martin Wosnik\textsuperscript{1,\Yinyang},
Budi Gunawan\textsuperscript{2,\textcurrency a},
Vincent Neary\textsuperscript{2,\ddag}
\\
\bigskip
\bf{1} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bf{2} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip
